# Região Norte 
 
## Acre 
 
```{r } 
 plot.seman("AC") 
``` 
 
## Amazonas 
 
```{r } 
 plot.seman("AM") 
``` 
 
## Amapá 
 
```{r } 
 plot.seman("AP") 
``` 
 
## Pará 
 
```{r } 
 plot.seman("PA") 
``` 
 
## Rondônia 
 
```{r } 
 plot.seman("RO") 
``` 
 
## Roraima 
 
```{r } 
 plot.seman("RR") 
``` 
 
## Tocantins 
 
```{r } 
 plot.seman("TO") 
``` 
 
# Região Nordeste 
 
## Alagoas 
 
```{r } 
 plot.seman("AL") 
``` 
 
## Bahia 
 
```{r } 
 plot.seman("BA") 
``` 
 
## Ceará 
 
```{r } 
 plot.seman("CE") 
``` 
 
## Maranhão 
 
```{r } 
 plot.seman("MA") 
``` 
 
## Paraíba 
 
```{r } 
 plot.seman("PB") 
``` 
 
## Pernambuco 
 
```{r } 
 plot.seman("PE") 
``` 
 
## Piauí 
 
```{r } 
 plot.seman("PI") 
``` 
 
## Rio Grande do Norte 
 
```{r } 
 plot.seman("RN") 
``` 
 
## Sergipe 
 
```{r } 
 plot.seman("SE") 
``` 
 
# Região Sudeste 
 
## Espírito Santo 
 
```{r } 
 plot.seman("ES") 
``` 
 
## Minas Gerais 
 
```{r } 
 plot.seman("MG") 
``` 
 
## Rio de Janeiro 
 
```{r } 
 plot.seman("RJ") 
``` 
 
## São Paulo 
 
```{r } 
 plot.seman("SP") 
``` 
 
# Região Sul 
 
## Paraná 
 
```{r } 
 plot.seman("PR") 
``` 
 
## Rio Grande do Sul 
 
```{r } 
 plot.seman("RS") 
``` 
 
## Santa Catarina 
 
```{r } 
 plot.seman("SC") 
``` 
 
# Região Centro-Oeste 
 
## Distrito Federal 
 
```{r } 
 plot.seman("DF") 
``` 
 
## Goiás 
 
```{r } 
 plot.seman("GO") 
``` 
 
## Mato Grosso do Sul 
 
```{r } 
 plot.seman("MS") 
``` 
 
## Mato Grosso 
 
```{r } 
 plot.seman("MT") 
``` 
 
