# Região Norte 
 
## Acre 
 
```{r } 
 plota2("AC") 
``` 
 
## Amazonas 
 
```{r } 
 plota2("AM") 
``` 
 
## Amapá 
 
```{r } 
 plota2("AP") 
``` 
 
## Pará 
 
```{r } 
 plota2("PA") 
``` 
 
## Rondônia 
 
```{r } 
 plota2("RO") 
``` 
 
## Roraima 
 
```{r } 
 plota2("RR") 
``` 
 
## Tocantins 
 
```{r } 
 plota2("TO") 
``` 
 
# Região Nordeste 
 
## Alagoas 
 
```{r } 
 plota2("AL") 
``` 
 
## Bahia 
 
```{r } 
 plota2("BA") 
``` 
 
## Ceará 
 
```{r } 
 plota2("CE") 
``` 
 
## Maranhão 
 
```{r } 
 plota2("MA") 
``` 
 
## Paraíba 
 
```{r } 
 plota2("PB") 
``` 
 
## Pernambuco 
 
```{r } 
 plota2("PE") 
``` 
 
## Piauí 
 
```{r } 
 plota2("PI") 
``` 
 
## Rio Grande do Norte 
 
```{r } 
 plota2("RN") 
``` 
 
## Sergipe 
 
```{r } 
 plota2("SE") 
``` 
 
# Região Sudeste 
 
## Espírito Santo 
 
```{r } 
 plota2("ES") 
``` 
 
## Minas Gerais 
 
```{r } 
 plota2("MG") 
``` 
 
## Rio de Janeiro 
 
```{r } 
 plota2("RJ") 
``` 
 
## São Paulo 
 
```{r } 
 plota2("SP") 
``` 
 
# Região Sul 
 
## Paraná 
 
```{r } 
 plota2("PR") 
``` 
 
## Rio Grande do Sul 
 
```{r } 
 plota2("RS") 
``` 
 
## Santa Catarina 
 
```{r } 
 plota2("SC") 
``` 
 
# Região Centro-Oeste 
 
## Distrito Federal 
 
```{r } 
 plota2("DF") 
``` 
 
## Goiás 
 
```{r } 
 plota2("GO") 
``` 
 
## Mato Grosso do Sul 
 
```{r } 
 plota2("MS") 
``` 
 
## Mato Grosso 
 
```{r } 
 plota2("MT") 
``` 
 
[1] "/home/paulo/work/pesquisa/colaboracoes/ift/corona/covid19br_repos/central_covid/scripts_R_genericos/InfoGripe"
